### 2016-05-09 ch02-qlogms/excitation-design.tex
Reset acronyms etc. per chapter
Diction on CH06

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}

@@

\item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007,Goodwin2006GBO,Rojas2012} and references therein. 
While the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
E.g. the approach followed by~\citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
As such, this requires more advanced prior knowledge of the system to cope with the uncertainty of the prior knowledge.
\end{enumerate}

\subsection{General Purpose Robust Excitation Signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

>>>>

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\glsresetall
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}

@@

\item Robust (optimal) input design makes the input design robust to uncertainty in the prior knowledge of the parameter values, see e.g.~\citep{Rojas2007,Goodwin2006GBO,Rojas2012} and references therein. 
Although the signal is more robust towards uncertainty in the prior knowledge, it requires more forethought than (nominal) optimal designs.
E.g. the approach followed by~\citet{Rojas2007} relies on both nominal parameter values and  knowledge of the distribution function of these parameters to design a robust (optimal) excitation signal.
As such, this requires more advanced prior knowledge of the system to cope with the uncertainty of the prior knowledge.
\end{enumerate}

\subsection{General Purpose Robust Excitation Signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is, however, not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

### 2016-05-09 ch06-concl/conclusions.tex
Reset acronyms etc. per chapter
Diction on CH06

\chapter{Conclusions}
\myEpigraph{Life can only be understood backwards; but it must be lived forwards.}{Søren Kierkegaard}{}
\tikzsetfigurename{ch06fig}

@@

  \subsection{Non-Parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.

@@

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to an initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.

>>>>

\chapter{Conclusions}
\myEpigraph{Life can only be understood backwards; but it must be lived forwards.}{Søren Kierkegaard}{}
\tikzsetfigurename{ch06fig}
\glsresetall

@@

  \subsection{Non-Parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, ongoing research focuses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.

@@

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to an initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This does not do away with the model order selection of the initial model, but it will improve the computational efficiency since fewer parameters are needed to approximate a particular system.
